Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-10 paper.qmd
Updated Figure 9b (a1)

@@

free(distance_points) /
  wrap_plots(trimesh_two_curvy2, trimesh_two_curvy_removed2, trimesh_two_curvy_removed1, two_curvy_proj_umap_model_delaunay, two_curvy_proj_umap_model_benchmark2, two_curvy_proj_umap_model, ncol = 3) +
  plot_annotation(tag_levels = list(c("(a)", "(b)")))

>>>>

trimesh_two_curvy <- ggplot() +
  geom_segment(data = tr_from_to_df_two_curvy,
               aes(
                 x = x_from,
                 y = y_from,
                 xend = x_to,
                 yend = y_to),
               colour = "#000000") +
  geom_point(data = tsne_two_curvy_scaled,
             aes(
               x = tSNE1,
               y = tSNE2
             ),
             color = "#636363",
             alpha = 0.5,
             size = 0.5
  ) +
  coord_equal() +
  interior_annotation("a1", sc_ltr_pos)

@@

free(distance_points) /
  wrap_plots(trimesh_two_curvy, trimesh_two_curvy_removed2, trimesh_two_curvy_removed1, two_curvy_proj_umap_model_delaunay, two_curvy_proj_umap_model_benchmark2, two_curvy_proj_umap_model, ncol = 3) +
  plot_annotation(tag_levels = list(c("(a)", "(b)")))
